% LaTeX file for resume 
% This file uses the resume document class (res.cls)
\let\nofiles\relax

\documentclass[overlapped]{res} 
% the margin option causes section titles to appear to the left of body text 
\textwidth=6.5in % increase textwidth to get smaller right margin
\resumewidth=6.6in %increase textwidth to get smaller right margin
\usepackage[utf8]{inputenc}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
\usepackage{newcent}   % uses new century schoolbook postscript font 

\usepackage{fancyhdr}
\usepackage[colorlinks=true]{hyperref}
\usepackage{helvetica}
%\usepackage{lastpage}
\fancypagestyle{firstpage}
{
    \fancyhead[L]{}    
    \fancyhead[R]{ {\huge \bf{Jonatan Jönsson}} \hfill Henrikdalsringen 73\\13132 Stockholm, Sweden\\
    +46 705 475 383 / \href{mailto:jontejj@gmail.com}{jontejj@gmail.com}\\ 
    \href{http://jontejj.github.io/resume/}{jontejj.github.io/resume} / 
    \href{http://linkedin.com/in/jonatanjoensson}{linkedin.com/in/jonatanjoensson}}
}
\thispagestyle{firstpage}
%\pagestyle{fancy}

%\rhead 

\renewcommand{\headrulewidth}{0pt} % Removes the horizontal line between header and page

\addtolength{\headheight}{\baselineskip}
\textheight 10.0in
\newsectionwidth{0.1in}

%\cfoot{\thepage\ of \pageref{LastPage}} doesn't work with the hyperref package
\begin{document} 
\begin{resume}
\vspace{1.2cm}
\section{{\sc RESEARCH}} 

{\bf Cellworld Simulation} \hfill May '24 - Present\\
\begin{itemize}
\itemsep -1pt
\item Designing and implementing a biologically inspired simulation environment modeling cell interactions, signaling, and emergent behavior. Developed a physics-based multicellular system in Java using dyn4j to simulate spatial dynamics and resource constraints. Exploring mechanisms for complex behavior and learning in distributed systems as a foundation for artificial general intelligence (AGI), supported by an extensible codebase for experimentation with neural development and adaptive behaviors.\\
\\{\bf Keywords} Java 25, dyn4j, Machine Learning, Artificial Intelligence
\end{itemize}

\section{{\sc EDUCATION}}

{\bf Bachelor's Degree} in Molecular Biology \hfill Aug '21 - May '24\\
{\sl from Stockholm University}

{\bf Bachelor's Degree} in International Software Engineering \hfill Sep '07 - Jun '10\\
{\sl from Blekinge Institute of Technology}

{\bf Exchange Student} in Computer Science \hfill Aug '09 - Dec '09\\
{\sl at Georgia Institute of Technology}
\begin{itemize}
\itemsep -1pt
\item {\bf Multicore and GPU programming for Video Games}\\ 3D engine in MATLAB, Xbox 360 (XNA), Playstation 3 (Cell), Shaders 
\item {\bf Computer and Network Security}\\ Implemented DES, AES, IDEA and Diffie Hellman in C++
\item {\bf Introduction to Artificial Intelligence}\\ Tournament winner in writing an AI player (in LISP) \\for the board game called Isolation
\item {\bf Computer and Society} \\ Wrote an essay about robot rights
\end{itemize}

{\bf  IT-Programme} with focus on network\hfill Aug '04 - Jun '07\\
{\sl at the John Bauer Gymnasium in Hässleholm}
\begin{itemize}
\itemsep -1pt
\item {\bf Student of the Year}  -- ``For excellent study results, a positive ambition and \\comradely behavior"
\end{itemize}

\section{{\sc WORK EXPERIENCE}} 

{\bf Research Traineeship in Biology} \hfill Nov '23\\
{\sl at SciLifeLab in Stockholm}
\begin{itemize}
\itemsep -1pt
\item Developed \href{https://github.com/jontejj/mirdeepsquared}{$mirdeep^2$} that uses a deep learning model to predict if novel miRNA sequences in the output of miRDeep2 are false positives or not.
\\{\bf Keywords} Python, Keras, Machine learning, Deep learning, AI
\end{itemize}
 

{\bf Software Engineer} \hfill Apr '18 - Aug '21 \\
{\sl at Peltarion AB in Stockholm}
\begin{itemize}
\itemsep -1pt
\item {\bf AI everywhere advancing humankind} Peltarion provides an operational AI platform for producing real-world AI applications at scale and at speed.
\\{\bf Keywords} Java 11, Keras, TensorFlow, Deeplearning4j, GCP (Google Cloud Platform),
\\Machine learning, Deep learning, AI
\end{itemize}

\vspace{0.8cm}
\centerline{1 of 3}
\newpage

{\bf Software Architect} \hfill Nov '14 - Apr '18 \\
{\sl at Nox Finans AB in Malmö}
\begin{itemize}
\itemsep -1pt
\item Automating invoice and debt collection processes. Broke even in 2016-04. 
\\A subsidiary company started by \href{http://www.fortnox.se/}{Fortnox}. Called Fortnox Finans today.
\\{\bf Keywords} Java 8, Dropwizard, Hibernate, Guice, Jersey, JAX-RS, PostgreSQL,
\\H2, MSSQL, Git, Gerrit, Jira
\end{itemize}

{\bf Software Developer} \hfill Sep '14 - Okt '14 \\
{\sl at Sony Mobile Communications AB in Lund}
\begin{itemize}
\itemsep -1pt
\item Helped maintain and evolve \href{http://emma.extranet.sonyericsson.com/emma/}{EMMA}.  A client used by service centers to flash 
\\mobile phones.
\\{\bf Keywords} Java, OSGi, Eclipse RCP 
\end{itemize}

{\bf Software Engineer} Consultant \hfill Nov '10 - Aug '14 \\
{\sl for Softhouse Consulting Baltic AB in Karlskrona}
\begin{itemize}
\itemsep -1pt
\item \href{http://www.fortnox.se/}{Fortnox} in Växjö \hfill Jun '14 - Aug '14
\\Fortnox helps more than 200,000 small business owners with their adminstration. 
\\Their system keeps track of invoices, payments, accounting, payroll etc.
\\{\bf Keywords} Java 8, Dropwizard, Hibernate, Guice, Jersey, JAX-RS, Git, Gerrit, 
\\Jira, PostgreSQL, MSSQL
\\
\itemsep -1pt
\item International Software Technology in Växjö \hfill Jan '14 - Jun '14
\\IST develops software aimed to help primary/high schools administer teachers, 
\\students, grades, curriculums and more.
\\{\bf Keywords} Java, Spring, Spring-Webflow, Tomcat, AngularJS, bower, grunt, Javascript
\\
\item \href{http://www.youtube.com/watch?v=htalgZCFWMI}{How To Clean Your Dirty Code}, Lightning talk at Leantribe in Växjö \hfill 2012-12-10
\\{\bf Keywords} Presentation,  Refactoring,  Clean Code,  Mutation Testing,  API design

\item \href{https://github.com/jontejj/how-to-clean-your-dirty-code}{How To Clean Your Dirty Code}, Softhouse Campus seminar \hfill 2012-11-29
\\{\bf Keywords} Course lecturer,  Clean Code
\\
\item Spielo/Gtech/BossMedia in Växjö
    \begin{itemize}
    \itemsep -1pt
    \item Gaming Management System (\href{http://www.spielog2.com/products/spielo-g2-gaming-management-system-(gms).aspx}{GMS}) \hfill Jan '13 - Jan '14
    \\GMS is the core in Spielos eco-system and is used  by users in
    \\150 countries. It handles player finances, responsible gaming and more.  
    \\{\bf Technologies} Game Platform, Java, Spring, Guava, Hibernate, JIRA, 
    \\Subversion, Jenkins, Ant, JBoss, Wildfly
    \itemsep -1pt
    \item Adding new features to a poker platform that for example \hfill Apr '12 - Okt '12 
    \\ \href{http://www.svenskaspel.se/poker}{Svenska Spel} and \href{http://www.ipnpoker.com/}{IPN} is using.  As we finished in 2 months instead of 6 
    \\we got to work on their new java-based server as well.
    \\{\bf Technologies} Poker, C++, Sybase, Boost, C\#, ASP.NET, 
    \\Internationalization, i18n, iPad, Java, Protobuf, Riak, Maven, JIRA
    \end{itemize}

\vspace{3.8cm}
\centerline{2 of 3}
\newpage

\item \href{http://www.ericsson.com}{Ericsson's Charging System} (the Service Data Point part)
\\A system for real-time rating of pre-paid calls, handling 1.4 billion subscribers.
\begin{itemize}
\itemsep -1pt
\item Product Customization Developer \hfill Aug '11 - Apr '12
    \\Added support for IMS (IP Multimedia System)
    \\{\bf Technologies} Geographically distributed team, Telecom, IMS, Java, Git,
    \\Gerrit, Jenkins, SCONS, TimesTen, Solaris, Scrum
\item Design \& Maintenance \hfill Nov '10 - Aug '11
    \\Solved several critical bugs that caused the system to grind to a halt.
    \\{\bf Technologies} Telecom, Bug-squashing, Java, C++, Clearcase, 
    \\Reviewboard.org, Hudson, SCONS, TimesTen, Solaris, Kanban
\end{itemize}
\end{itemize}

{\bf Software Developer} Project employment \hfill Jun '10 - Okt '10 \\
{\sl at BTH Innovation in Ronneby}
\begin{itemize}
\itemsep -1pt
\item Developed an iPhone version of Hanashi (Chat application), for Sony Ericsson 
\\Mobile Communications. This was a continuation of our graduation project. 
\\I was the first (among 10 other team members) to be selected to continue the project.
\\Since then the app has been removed but while in App Store Nordic it 
\\only received 5-star reviews.
\\{\bf Technologies} Instant Messaging, Objective-C, iOS SDK, APNS, Java, Scrum
\end{itemize}

\section {{\sc SKILLS} - {\sl From high to low}}
{\bf Solid skills with} Java, Python, SQL, Javascript, HTML, CSS, C\#, C++, Objective-C, PHP\\
{\bf Have used} C, .NET, APS.NET, LISP, Riak, Sybase, TimesTen, CG, Assembler (MIPS), MATLAB, KSH, TCSH, TTCN3 \\
{\bf Frameworks} Keras, TensorFlow, AngularJS, Guava, Spring, Hibernate, Django, SDL, iOS SDK, XNA, Boost, Protobuf \\
{\bf Operating Systems} Mac OS X, Windows, Ubuntu, Solaris\\
{\bf Tools} Eclipse, Maven, bower, grunt, Ant, Webstorm, XCode, Visual Studio, JIRA\\
{\bf Processes} TDD, Pair Programming, Code reviews, Kanban, Scrum, XP\\
{\bf VCS} Git, Subversion (SVN), Mercurial (HG), ClearCase\\
{\bf Spoken Languages} Native in swedish, fluent in english, limited in german, limited in russian \\

\vspace{7.6cm}
\centerline{3 of 3}
%\end{description}
\end{resume} 
\end{document} 
% Keywords: Software Engineer, Bachelor's Degree, Ericsson Charing System, SDP, iPhone, XNA, SDL, c++, Java, Objective-C, PHP
